\begin{enumerate}[label=\arabic*.,ref=\theenumi]
\item In a given $8$-bit general purpose micro-controller there are following flags. $C$-Carry, $A$-Auxiliary Carry, $O$-Overflow flag, $P$-Parity ($0$ for even, $1$ for odd) $R0$ and $R1$ are the two general purpose registers of the micro-controller.After execution of the following instructions, the decimal equivalent of the binary sequence of the flag pattern $[CAOP]$ will be $\underline{\hspace{1cm}}$.\\


\begin{lstlisting}
MOV R0,+0x60
MOV R1,+0x46 
ADD R0,R1
\end{lstlisting}
    
\hfill{(EE GATE 2023)}\\


\item 
Consider the given C-code and its corresponding assembly code, with a few operands U1-U4 being unknown. Some useful information as well as the semantics of each unique assembly instruction is annotated as inline comments in the code.

\begin{lstlisting}
int a[10],b[10],i;
//int is 32-bit
for (i=0;i<10;i++)
a[i]=b[i]*8;
\end{lstlisting}

\begin{lstlisting}
;r1-r5 are 32-bit integer registers
;initialize r1=0,r2=0
;initialize r3,r4 with base address of a,b

L01:jeq r1,r2,end ;if(r1==r2) goto end
L02:lw r5,0(r4)   ;r5<-Memory[r4+0]
L03:shl r5,r5,U1  ;r5<-r5<<U1
L04:sw r5,0(r3)   ;Memory[r3+0]<- r5
L05:add r3,r3,U2  ;r3<-r3+U2
L06:add r4,r4,U3
L07:add r1,r1,1
L08:jmp U4        ;goto U4
L09:end
\end{lstlisting}

\item Which one of the following options is a CORRECT replacement 
for operands in the position (U1,U2,U3,U4) in the above 
assembly code?

\begin{enumerate}
\item (8,4,1,L02)                      
\item (3,4,4,L01)
\item (8,1,1,L02)                             
\item (3,1,1,L01)         
\end{enumerate}
\item An $8085$ microprocessor accesses two memory locations $\brak{2001H}$ and $\brak{2002H}$, that contain $8$-bit numbers $98$H and $B1$H, respectively.The following program is executed:
\begin{verbatim}LXI H,2001H
MVI A,21H
INX H
ADD M
INX H
MOV M,A
HLT
\end{verbatim}
At the end of this program, the memory location $2003$H contains the number in decimal $\brak{base 10}$ form $\underline{\hspace{2cm}}$.

$\hfill\brak{GATE\enspace EE2020-54}$
\item  Which of the following is the correct binary equivalent of the hexadecimal F6C?
$\hfill\brak{GATE\enspace PH2020,6}$

\begin{enumerate}
  \item  $0110 1111 1100$
  \item $1111 0110 1100$
  \item $1100 0110 1111$
  \item $0110 1100 0111$

\end{enumerate}
\item
\label{prob:gate IN 45}
 A portion of an assembly language program written for an $8$-bit microprocessor is given below along with explanations. The code is intended to introduce a software time delay. The processor is driven by a $5$ MHz clock. The time delay (in $\mu$s) introduced by the program is \vspace{12 pt}


MVI B, $64$H; Move immediate the given byte into register B. Takes $7$ clock periods.\vspace{12 pt}


LOOP: DCR B ; Decrement register B. Affects Flags. Takes $4$ clock periods. \vspace{12 pt}


JNZ LOOP ; Jump to address with Label LOOP if zero flag is not set. Takes $10$ clock periods when jump is performed and $7$ clock periods when jump is not performed.

\hfill(GATE IN 2018)

\item A $10\frac{1}{2}$ digit Counter-timer is set in the 'frequency mode' of operation (with $T_s=1s$). For a specific input, the reading obtained is $1000$. Without disconnecting this input, the Counter-timer is changed to operate in the 'Period mode' and the range selected is microseconds ($\mu$s,with $f_s=\SI{1}{\mega\hertz}$).The Counter Will then display
\hfill(GATE IN 2021)
\begin{enumerate}
  \item $0$
  \item $10$
  \item $100$
  \item $1000$
\end{enumerate}

\item Consider three registers $\textbf{R1 ,R2 ,R3}$ that store numbers in $ IEEE-754 $ single precision floating point format. Assume that $\textbf{R1}$ and $\textbf{R2}$ contain the values (in hexadecimal notation) $0\textbf{x}42200000$ and $0\textbf{x}C1200000,$ respectively. If $ \textbf{R3}=\frac{\textbf{R1}}{\textbf{R2}} $, what is the value stored in $\textbf{R3}?$
\hfill(GATE-EC2021,31)
\begin{enumerate}
    \item 0x40800000
    \item 0xC0800000
    \item 0x83400000
    \item 0xC8500000
\end{enumerate}

\item The content of the registers are $R_1 = 25H$, $R_2 = 30H$ and $R_3 = 40H$. The following machine instructions are executed.
\begin{align*}
  PUSH \cbrak {R_2}  
  \\PUSH \cbrak {R_2}
  \\PUSH \cbrak {R_3} 
  \\POP \cbrak {R_1} 
  \\POP \cbrak {R_2} 
  \\POP \cbrak {R_3} 
\end{align*}

After execution, the content of registers $R_1$, $R_2$, $R_3$ are
\hfill(GATE-EC2021,32)

\begin{enumerate}
    \item $R_1 = 40H, R_2 = 30H,R_3 = 25H$
    \item $R_1 = 25H, R_2 = 30H,R_3 = 40H$
    \item $R_1 = 30H, R_2 = 40H,R_3 = 25H$
    \item $R_1 = 40H, R_2 = 25H,R_3 = 30H$
\end{enumerate}



\end{enumerate}
